### 2020-02-14 acknowledgements.tex
Shervin signed (no critiques). Re-read Chp 1.
changed a bit after OT

  First and foremost, I thank Professor Luca Brandt for accepting me in and guiding me through the PhD program at KTH Mechanics.
  His strong leadership from the inception,
  enthusiastic responses and constructive criticisms at every discussion,
  generous support and increasing trust in me towards the end are indispensable for me to grow and develop academically.
  For these reasons, I owe my deepest gratitude to him.

  Second, I wish to extend my sincere thanks to my day-to-day advisors and mentors at KTH.
  I thank Outi Tammisolar for co-advising me since my first project, following my progress throughout the PhD
  and offering me invaluable career advice in the later years.
  I thank Jean-Christophe Loiseau for instilling in me the European culture, proper programming and mathematical rigour.
  I also thank Mehdi Niazi for always being available for technical discussions or code debugging and sharing his wisdom whenever I am lost.
  The patience, support and encouragement they offered me are instrumental in building my confidence and independence, which I will never take for granted.

  Third, I want to express my appreciation to all collaborators and senior colleagues that have shaped and contributed to my PhD work.
  These include, but are not limited to, international collaborators: Michael Dodd, Alexander Leshansky, Itzhak Fouxon and Naoki Takeishi;
  former and present colleagues at KTH: Walter Fornari, Pedro Costa, Francesco de Vita, Marco Rosti, B. M. Ningegowda and U\'{g}is L\={a}cis;
  office mates: Ricardo Vinuesa, Ekaterina Ezhova, Tímea Kékesi, Arash Alizad Banaei and Ashwin Vishnu;
  and professors that I enjoy talking to or playing innebandy with:
  Shervin Bagheri, Christophe Duwig, Hanno Essén, Nicholas Apazidis, Lanie Gutierrez-Farewik and Fredrik Lundell.
  Many others have also helped, corrected or inspired me in various research projects;
  my thanks are expressed in the separate acknowledgements after each paper in the next part of the thesis.

  In his famous essay, \emph{\small The World As I See It}, Einstein wrote,
  ``But from the point of view of daily life, without going deeper, we exist for our fellowmen --
  in the first place for those on whose smiles and welfare all our happiness depends,
  and next for all those unknown to us personally with whose destinies we are bound up by the tie of sympathy.''
  In the last several years, I have been lucky to derive plentiful happiness and sympathy from Artem, Erik, Guillaume, Nicolas, Frida, Natasha, Thea, Lee,
  as well as the rest of the Roslagstullsbacken corridor.
  Particularly, I am blessed to meet Dia, whose courage, ambition, curiosity and sensitivity have become a continuing source of my attachment,
  making me feel thorough and complete.

  Finally, none of the above would have been possible without the enduring love, hope, protection and education from my family at home.

>>>>

  First and foremost, I thank Professor Luca Brandt for accepting me in and guiding me through the PhD program at KTH Mechanics.
  His strong leadership from the inception,
  enthusiastic responses and constructive criticisms at every discussion,
  generous support and increasing trust in me towards the end are indispensable for me to grow and develop academically.
  For these reasons, I owe him a debt of gratitude.

  Second, I wish to extend my sincere thanks to my day-to-day advisors and mentors at KTH.
  I thank Outi Tammisolar for co-advising me since my first project, following my progress throughout the PhD
  and offering me invaluable career advice in the later years.
  I thank Jean-Christophe Loiseau for instilling in me the European culture, proper programming and mathematical rigour.
  I also thank Mehdi Niazi for always being available for technical discussions or code debugging and sharing his wisdom whenever I am lost.
  The patience, support and encouragement they offered are instrumental in building my confidence and independence, which I will never take for granted.

  Third, I want to express my appreciation to all collaborators and senior colleagues that have shaped and contributed to my PhD work.
  These include, but are not limited to, international collaborators: Michael Dodd, Alexander Leshansky, Itzhak Fouxon and Naoki Takeishi;
  former and present colleagues at KTH: Walter Fornari, Pedro Costa, Lailai Zhu, Francesco de Vita, Marco Rosti, Sagar Zade, B. M. Ningegowda, U\'{g}is L\={a}cis and Oleksiy Klurman;
  office mates: Ricardo Vinuesa, Ekaterina Ezhova, Tímea Kékesi, Arash Alizad Banaei and Ashwin Vishnu;
  and professors that I enjoy talking to or playing innebandy with:
  Shervin Bagheri, Christophe Duwig, Hanno Essén, Lanie Gutierrez-Farewik, Ruoli Wang and Fredrik Lundell.
  Many others have also helped, corrected or inspired me in various research projects;
  my thanks are expressed in the separate acknowledgements after each paper in the next part of the thesis.

  In his essay \emph{\small The World As I See It}, Einstein wrote,
  ``But from the point of view of daily life, without going deeper, we exist for our fellowmen --
  in the first place for those on whose smiles and welfare all our happiness depends,
  and next for all those unknown to us personally with whose destinies we are bound up by the tie of sympathy.''
  In the last several years, I have been lucky to derive plentiful happiness and sympathy from Artem, Erik, Guillaume, Nicolas, Frida, Natasha, Thea, Lee,
  as well as the rest of the Roslagstull corridor.
  Particularly, I am blessed to meet Dia, whose courage, ambition, curiosity and sensitivity have become a continuing source of my attachment,
  making me feel thorough and complete.

  Finally, none of the above would have been possible without the enduring love and education from my family at home.

### 2020-02-14 overview.tex
changed a bit after OT

All the above-mentioned processes or technologies depend on the presence and motion of droplets.
Understanding the physics and hydrodynamics of their interactions in a variety of conditions thus has a great practical importance.
Traditionally, the study of liquid-embedded systems are mostly conducted by experimenters;
fluid mechanics, as most other disciplines of physics, is primarily an experimental science after all.
However, the last few decades have also seen a phenomenal paradigm shift in many research areas owing to
the exponential growth of computer power and continuous development of numerical algorithms.
Fluid dynamics is now in the vanguard of applying large-scale computations in resolving natural and engineering problems and is,
in turn, pushing the boundary of computer science.
Comparing to experimental measurements, computer simulations are non-invasive and
offer the entire information that can be readily visualised up to model errors and the numerical precision.
Physical parameters can also be freely adjusted to test conditions that are not easy to implement in lab experiments.

Motivated by these reasons, the present work embarks on a number of problems that originates from material fabrication, surface engineering and fluid transport.
We develop and utilise both high- and low-fidelity numerical models to simulate the underlying processes with the aims of
complementing experimental studies and elucidating their physical mechanisms.
The common ground at the bottom of these enquiries is that the processes all entail interactions of droplets in an ambient fluid or
are governed by the dynamics near a fluid interface.
Their specific backgrounds are given below (see also Chapter \ref{chp:misc}).

@@

\medskip
In partial response to the challenge, we numerically explore dense suspensions under different imposed flow conditions and geometric constraints.
In particular, we study particles in the noncolloidal regime, and ask:
(i) how to minimally characterise the microstructural evolution in an unsteady flow?
Candidate answers include the (complex) suspension viscosity, particle diffusivity, suspension fabric, size distribution of local hydroclusters, structure factor, \etc \citep{Brady_Bossis1988, Sal03, Ness_Xing_Eiser_2017}.
(ii) Can qualitatively different global behaviours, such as a rate-dependent rheology vs.\ a rate-independent rheology,
occur to the same suspension under different flow protocols? And
(iii) how does the particle geometry affect the rheology and jamming of a suspension at fixed volume fractions?
Solving these problems requires a numerical methodology that is accurate enough to test different physical hypotheses and
efficient enough to generate data for a wide range of parameters.
The implementation details of one such algorithm is documented in \emph{Paper 7}.

@@

\medskip
When the suspension is non-dilute, normal stresses can deviate from each other as a result of the anisotropic microstructure or particle collision.
This leads to the definitions of the first and second normal stress differences as above, where $x$, $y$, $z$ denote the flow, velocity-gradient, and negative vorticity directions, respectively.
$N_1$ and $N_2$ are usually normalized by the modulus of the shear stress, $\abs{\bm{\Sigma}_{xy}}$, since they also diverge as $\phi \to \phi_J$.
The exact relationship between $N_1$ or $N_2$ and $\phi$ have not been clearly found. The overall picture is that $N_1$ is mostly of hydrodynamic origin, while $N_2$ is negative and large in magnitude due to particle collisions, which happen more frequently in the $xy$ plane \citep{guazzelli_pouliquen_2018}.
See \cite{seto_giusteri_2018} for further discussions.

>>>>

All the above-mentioned processes or technologies depend on the presence and motion of droplets.
Understanding the physics and hydrodynamics of their interactions in a variety of conditions thus has a great practical importance.
Traditionally, the study of liquid-embedded systems is mostly conducted by experimentalists;
fluid mechanics, as most other disciplines of physics, is primarily an experimental science after all.
However, the last few decades have also seen a phenomenal paradigm shift in many research areas owing to
the exponential growth of computer power and continuous development of numerical algorithms.
Fluid dynamics is now in the vanguard of applying large-scale computations in resolving natural and engineering problems and is,
in turn, pushing the boundary of computer science.
Comparing to experimental measurements, computer simulations are non-invasive and
offer the entire information that can be readily visualised up to model errors and the numerical precision.
Physical parameters can also be freely adjusted to test conditions that are not easy to implement in lab experiments.

Motivated by these, the present work embarks on a number of problems that originates from material fabrication, surface engineering and fluid transport.
We develop and utilise both high- and low-fidelity numerical models to simulate the underlying processes with the aims of
complementing experimental studies and elucidating their physical mechanisms.
The common ground at the bottom of these enquiries is that the processes all entail interactions of droplets in an ambient fluid or
are governed by the dynamics near a fluid interface.
Their specific backgrounds are given below (see also Chapter \ref{chp:misc}).

@@

\medskip
In partial response to the challenge, we numerically explore dense suspensions under different imposed flow conditions and geometric constraints.
In particular, we study particles in the noncolloidal regime, and ask:
How to minimally characterise the microstructural evolution in an unsteady flow?
How to relate the (complex) suspension viscosity -- a quantity that is routinely measured or calculated -- to other microscopic variables such as the particle diffusivity, suspension fabric or local density fluctuations \citep{Brady_Bossis1988, Sal03, Ness_Xing_Eiser_2017}?
How sensitive is the dependence of suspension behaviour on the details of the deformation (\ie shear or extensional flow, steady or transient flow, etc.)?
And how does the particle geometry affect the rheology and jamming of a suspension at fixed volume fractions?
Solving these problems requires a numerical methodology that is accurate enough to test different physical hypotheses and
efficient enough to generate data for a wide range of parameters.
The implementation details of one such algorithm is documented in \emph{Paper 7}.

@@

\medskip
When the suspension is non-dilute, normal stresses can deviate from each other as a result of the anisotropic microstructure or particle collision.
This leads to the definitions of the first and second normal stress differences as above, where $x$, $y$, $z$ denote the flow, velocity-gradient, and negative vorticity directions, respectively.
$N_1$ and $N_2$ are usually normalized by the modulus of the shear stress, $\abs{\bm{\Sigma}_{xy}}$, since they also diverge as $\phi \to \phi_J$.
The exact relationship between $N_1$ or $N_2$ and $\phi$ is unclear.
The overall picture is that $N_1$ is mostly of hydrodynamic origin, while $N_2$ is negative%
\footnote{Collision results in a negative normal stress because it is repulsive; the force is in the opposite direction to the position vector.}
and large in magnitude (\ie $|N_2| \gtrapprox |N_1|$) due to particle collisions, which happen more frequently in the $xy$ plane \citep{guazzelli_pouliquen_2018}.
See \cite{seto_giusteri_2018} for further discussions.
